Simulations of Ballot Polling Risk-Limiting Audits

### 2022-07-20 providence/sections/workload.tex
explaining

Consider the US state of Pennsylvania. In the 2020 US Presidential contest, Pennsylvania had a margin of $99999\%$.

@@

We now consider a simple round schedule for our example. Each round is selected to give the same probability of stopping, $p$. If the audit does not stop in the first round, we find a round size which, given the sample drawn in the first round, will give a probability of stopping $p$ in the second round. For this round schedule scheme, a one-and-done audit is achieved by choosing large $p$, say $p=.9$ or $p=.95$. For this particular round schedule scheme, computing the expected number of rounds is straightforward; . Our simulations are then used to estimate the expected number of ballots.

@@

Without extensive workload measurements, it is hard to know the most accurate value for $c_r$, and so we also evaluate the simulation results with varying $c_r$. 
For each $c_r$, we find the value of $p$ which minimizes the expected workload as we did in Figure~\ref{fig:workload}. Figure~\ref{fig:optimal_ps} presents, for varying $c_r$ the round schedule parameter $p$ which minimizes expected workload.

>>>>

Consider the US state of Michigan. In the 2020 US Presidential contest, Michigan had a margin of $2.8\%$.

@@

We now consider a simple round schedule for our example. Each round is selected to give the same probability of stopping, $p$. If the audit does not stop in the first round, we find a round size which, given the sample drawn in the first round, will give a probability of stopping $p$ in the second round. For this round schedule scheme, a one-and-done audit is achieved by choosing large $p$, say $p=.9$ or $p=.95$. For this particular round schedule scheme, computing the expected number of rounds is possible analytically(TODO: I worked it out, just need to add here). Our simulations are then used to estimate the expected number of ballots.

@@

Without workload measurements from multiple round audits, it is difficult to know an accurate value for $c_r$, and so we also evaluate the simulation results with varying $c_r$. 
For each $c_r$, we find the value of $p$ which minimizes the expected workload as we did in Figure~\ref{fig:workload}. Rather than use the minimum cost estimate among the sparsely sampled points, we fit a quadratic polynomial and use its minimum to get a smoother relationship between $c_r$ and optimal $p$. Figure~\ref{fig:optimal_ps} presents, for varying $c_r$ the round schedule parameter $p$ which minimizes expected workload. 
We observe that for a workload model with no overhead for each round (i.e. $c_r=0$), the optimal round schedule is that with $p=0.72$. As $c_r$ increases, the optimal value of $p$ also increases, up to as much as $p=.9$ for $c_r=10^4$.

Analysis like this can be used to select round schedules for audits.

% check that report to see if we can at least suggest what might be reasonable
